---
title: "HW 12"
author: "Yujui Chang"
date: "`r Sys.Date()`"
output: html_document
urlcolor: "blue"
params:
  solutions: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo       = params$solutions, 
                      eval       = params$solutions,
                      fig.align  = "center",
                      fig.height = 3, 
                      fig.width  = 5)
```

# Instructions

- Write your solutions in this starter file. You should modify the 
  "author" field in the YAML header.
- Do not modify the paths of any files.
- Only commit R Markdown and HTML files (no PDF or Word files). Make sure
  you have knitted to HTML for your final submission.
- **Make sure to commit each time you answer a question.** Lack of informative
  and frequent commits will result in point deductions.
- Only include the necessary code, not any extraneous code, to answer the 
  questions.
- Learning objectives:
    - Obtain data from an API.
    - Scrape data from the web.

# Open Brewery Database

Consider the Open Brewery Database API: <https://www.openbrewerydb.org/>

1. Get the list of all micro breweries in Ohio where we have longitude and
   latitude information. These should be the microbreweries you obtained:
```{r}
library(tidyverse)
library(httr)

qout <- GET(url = "https://api.openbrewerydb.org/breweries?by_state=ohio",
            query= list(by_type= "micro"))

brewer_list <- content(qout)

for(i in 1:length(brewer_list)){
  brewer_list[[i]]$name -> names(brewer_list)[i]
}
# give every list a name.

for(i in length(brewer_list):1){
  if(is.null(brewer_list[[i]]$longitude)){
    brewer_list[-i] -> brewer_list
  }else{
    next()
  }
}
# drop lists which longitude are NULL

names(brewer_list)

```
  
2. Clean up the data from part 1 to get the following data frame:
```{r}
brewer_df <- data.frame(matrix(unlist(brewer_list), nrow=length(brewer_list), byrow=T),stringsAsFactors=FALSE)
# combine list and change to dataframe

for(i in 1:13){
  names(brewer_df)[i] <- names(brewer_list[[1]][i])
}
# give name for each column

brewer_df %>%
  select(-brewery_type, -state, -country) %>%
  mutate(id = parse_number(id),
         longitude = parse_number(longitude),
         latitude = parse_number(latitude)
         ) ->
  brewer_df

brewer_df

```

3. Edit the following ggplot code to obtain the following plot:

```{r, eval = FALSE, echo = TRUE, fig.width = 4, fig.height = 4}
    library(maps)
    countymap <- map_data("county")
    
    brewer_df %>%
      select(longitude,latitude) %>%
      mutate(subregion = "adams") -> brewer_temp 
    names(brewer_temp)[1] <- "long"
    names(brewer_temp)[2] <- "lat"
    # mutate group column to brewer_temp
    
    countymap %>%
      filter(region == "ohio") %>%
      ggplot(aes(x = long, y = lat, group = subregion)) +
      geom_polygon(fill = "white", color = "black")+
      geom_point(data = brewer_temp, aes(x= long, y= lat))+
      theme(
          panel.grid = element_blank(),
          panel.background = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank()
      ) 
    # add plot
    
```

# English women artists

Consider the copied Wikipedia page on English women artists: 
<https://data-science-master.github.io/lectures/data/engart.html>

We'll use the copied version on GitHub rather than the original version
to make sure solutions are consistent. But the original version can be found
here (but don't use it): <https://en.wikipedia.org/wiki/List_of_English_women_artists>

Use rvest to answer the following questions.

1. Download the html file and save the output to a variable.
```{r}
library(rvest)
w_artist_web <- read_html("https://data-science-master.github.io/lectures/data/engart.html")

```

2. Use SelectorGadget to extract each woman, years of life, and artistic medium.
   For example, my selections looked like this:
```{r}
html_nodes(w_artist_web, css = "ul:nth-child(49) li , ul:nth-child(47) li, ul:nth-child(45) li, ul:nth-child(43) li, ul:nth-child(41) li, ul:nth-child(39) li, ul:nth-child(37) li, ul:nth-child(35) li, ul:nth-child(33) li, ul:nth-child(31) li, ul:nth-child(29) li, ul:nth-child(27) li, ul:nth-child(25) li, ul:nth-child(23) li, ul:nth-child(21) li, ul:nth-child(19) li, ul:nth-child(17) li, ul:nth-child(15) li, ul:nth-child(13) li, ul:nth-child(11) li, ul:nth-child(9) li, ul:nth-child(7) li, ul:nth-child(5) li") %>%
  html_text() ->
  womenlist

women_tab <- tibble(womenlist)

```

3. Clean the data. 

    Hints:

    1. Not all year ranges are of the form (Birth-Death). You should place
       NA's in the appropriate locations. No need to extract third-party 
       datasets to obtain the true values.
    2. Be careful of parsing numbers like `"c.1888"`.
    3. Parentheses are used more than just to delimit years.
    4. Painters, sculptors, illustrators, and printmakers are the most common
       types of artists, so I included indicators for those mediums. Note
       that not all printmakers are called "printmakers".

    Your final data frame should look like this:
```{r}
women_tab %>%
  mutate(womenlist = str_replace_all(womenlist, "\\n",""),
         artist = str_extract(womenlist, "^.*\\(|.*\\,"),
         artist = str_replace_all(artist, " \\(.*\\)|\\(", ""),
         artist = str_replace(artist,"r,|n,|y,","")) ->
  women_tab
# mutate artist column
women_tab %>%
  mutate(life = str_extract(womenlist, "\\(.*\\)"),
         life = str_replace_all(life, "\\([A-z]*\\)|\\([A-z]* [A-z]*\\)",""),
         life = str_replace(life, "born ", ""),
         life = str_replace(life, "fl.|c.|active",""),
         life = str_replace(life, "died ", "-"),
         life = str_replace(life, "\\( ","("),
         life = str_replace(life, "—|-","–"),
         life = str_replace_all(life, ",| [A-z]*", "")) ->
  women_tab
# fix birth & death

women_tab %>%
  mutate(birth = str_extract(life, "\\([0-9]+"),
         death = str_extract(life, ".[0-9]+\\)"),
         birth = str_replace(birth, "\\(", ""),
         death = str_replace(death, "\\([0-9]+\\)", ""),
         birth = parse_number(birth),
         death = parse_number(death)) %>%
  select(-life)->
  women_tab
# mutate birth & death

women_tab %>%
  mutate(mediums = str_extract(womenlist, "\\).*|,.*"),
         mediums = str_replace(mediums, "\\), ", ""),
         mediums = str_replace(mediums, ".+[0-9]+", ""),
         mediums = str_replace(mediums, ",|\\)", ""),
         mediums = str_replace(mediums, "date of death unknown",""),
         mediums = str_replace(mediums, "painting", "painter"),
         mediums = str_replace(mediums, "printer", "printmaker"),
         mediums = str_replace(mediums, "prıntmaker", "printmaker")) ->
  women_tab
# mutate mediums, painting = painter? , printer = printmaker, prıntmaker = printmaker
# page 14, painting = painter? / page 8 printer = printmaker? / page 6 prıntmaker = printmaker


women_tab %>%
  mutate(painter = str_detect(mediums, "painter"),
         sculptor = str_detect(mediums, "sculptor"),
         illustrator = str_detect(mediums, "illustrator"),
         printmaker = str_detect(mediums, "printmaker")) ->
  women_tab
# mutate painter, sculptor, illustrator, and printmaker

women_tab %>%
  select(-womenlist) ->
  women_tab

women_tab

```

4. Tabulate the number of painters, sculptors, illustrators, and printmakers.
   You should get these numbers:
```{r}
women_tab %>%
  summarize(painters_n = sum(painter),
            sculptor_n = sum(sculptor),
            illustrator_n = sum(illustrator),
            printmaker_n = sum(printmaker))
```

5. Plot the lifespans of printmakers. Your plot should look like this:
```{r}
library(ggthemes)

women_tab %>%
  arrange(birth,-death) %>%
  mutate(artist = parse_factor(artist),
         artist = fct_reorder(artist, -birth)) %>%
  select(artist, birth, death, painter, printmaker) %>%
  filter(printmaker == TRUE) ->
  pl

  ifelse(is.na(pl$death),Inf,pl$death[]) -> pl$death
  
  pl %>%
  ggplot(aes(x= birth, y= artist))+
  geom_segment(aes(x= birth, xend= death, y= artist, yend= artist, colour= painter),lwd = 1)+
  xlab("Birth/Death")+
  ylab("Artist")+
  theme_bw()+
  scale_color_colorblind()
  # Bacon and Fiennes should change position.
```

